\documentclass{letter}
\usepackage{hyperref}
\signature{Team \#39984}
\begin{document}

\begin{letter}{}
\opening{To whom it may concern,}


    After hearing about the exciting news that your association has developed a new kind of medication which are effective in curing and preventing Ebola disease, we are eager to use our modeling knowledge to help the association with the subsequent projects. 
    
    It is widely known that Ebola has broken out in the year 2014 and has been assaulting African people till now. So we first make a prediction about the cease time point of Ebola virus disease, making use of the statistics collected from World Health Organization. We predict that Ebola might stop its decimation by the end of 2015. Besides, we have made a model on predicting future increase of newly infected people, and we predict that in a half year period, there may be about 2134 more people infected by Ebola virus disease, and the specific statistics goes down to three countries are: Guinea 703 cases, Liberia 346 cases, and Sierra Leone 1085 cases.
    
    After serious consideration, we decide to give our suggestion on the site selection of medical center that your association will set in the epidemic areas sooner or later.
    
    Since these days Ebola disease has been minimizing its power and the number of newly increased cases is somehow declining, it is much easier now for you to manufacture medicine and vaccines than during the most terrible months in 2014. This means that only one medical center is needed as the efficiency may be augmented once delivery projects are assembled at a specific location so as to cut off those unnecessary expense on traffic and transport. What's more, it is obvious that the medical center's site should relate to the most seriously infected area, where the number of individuals is superior to other areas to some extent. In addition, the expense on traffic should also be considered when selecting the site. 
    
    Now it comes to the dispensation of vaccine and drug. In your association's announcement your developed medication contains two kinds of medical products, vaccine and drug. We all know that vaccine can effectively decrease the number of people who are likely to be infected. So as we boldly predict, if vaccine is put into use from now on, the number of infected people will cut off by (). As for drug, since till now the number of newly infected people has been slightly decreasing and the pressure on the pharmaceutical factory affiliated to your association will not be too high. As a matter of fact, we believe that your association has the ability to manufacture adequate drug for every single patient, so you can try to follow our model's prediction and distribute drug rationally according to the increase pattern of infected individuals in diverse areas.
    
    In a word, your association has made magnificent contribution to medical academic world as well as brought living hope to the African people struggling against pain and death. We are sure that your association will help decrease the death resulted by Ebola to a great extent. We are looking forward to hearing good news from you. Our advice, if proved to be useful, may accelerate your process of eradicating the Ebola virus disease, and we will also keep our pace to dedicate more into modeling so as to try our best to provide further assistance. 



\closing{Yours Faithfully,}


\end{letter}
\end{document}